The imprint of global magma oceans on exoplanet demographics

### 2022-09-08 src/tex/ms.tex
Minor edits, mostly describing methods

    Here, we assess the ability of space and ground-based telescopes to test this hypothesis using Bioverse, a simulation framework that leverages contextual information from the overall planet population.
    We argue that in the near future, ESA's PLATO mission and NASA's Roman Space Telescope will be the most promising endeavors to constrain this demographic feature.
    For each of these missions, we identify the key mission design drivers that enable a statistically sound detection.
    We also show the unique synergy of these missions in answering this question, and what survey strategy optimizes the statistical power of the combined dataset.

    $\ldots$ its measurement will also provide insights into which stars harbor the nearest habitable worlds.
\end{abstract}

@@

\Blindtext[1]

@@

\subsection{Testing the magma ocean hypothesis with current and planned exoplanet missions}
\todo{Introduce survey simulation(s). PLATO, Ariel, LIFE?, Nautilus\\ What are threshold missions that are able to detect this signal? =>X meter working for Y years, or X' meter working for Y' years => conclusion could be that there is interesting science to do with intermediate size telescope.}
\begin{note}
    In previous steps, we generated a population of synthetic planets that orbit synthetic stars, and we have injected the statistical trend expected from the presence of magma oceans on a fraction of the planets.
    Only a subset of these planets would be detectable by a transit survey, and their properties can be probed only with a finite precision.
    To test the detectability of a magma ocean signature, we simulated several transit surveys with different designs and strategies and explored their ability to recover the magma ocean trend and constrain its parameters.

    We consider a number of key parameters of transit surveys: The telescope's mirror diameter (or effective diameter for a telescope array) $D$, the total time budget of the survey for observations $t_\mathrm{total}$, the maximum number of observed transits for each target $N_\mathrm{obs, max}$, the slew time between observations $t_\mathrm{slew}$, ...

>>>>

    Here, we assess the ability of space and ground-based telescopes to test this hypothesis using Bioverse, a simulation framework that leverages contextual information from the overall planet population.
    $\ldots$

%    We argue that in the near future, ESA's PLATO mission and NASA's Roman Space Telescope will be the most promising endeavors to constrain this demographic feature.
%    For each of these missions, we identify the key mission design drivers that enable a statistically sound detection.
%    We also show the unique synergy of these missions in answering this question, and what survey strategy optimizes the statistical power of the combined dataset.
%    $\ldots$ its measurement will also provide insights into which stars harbor the nearest habitable worlds.
\end{abstract}

@@

@@

\subsection{Testing the magma ocean hypothesis with current and planned exoplanet missions}
\todo{Introduce survey simulation(s). PLATO, Ariel, LIFE?, Nautilus\\ What are threshold missions that are able to detect this signal? =>X meter working for Y years, or X' meter working for Y' years => conclusion could be that there is interesting science to do with intermediate size telescope.}
\begin{note}
    In previous steps, we generated a population of synthetic planets that orbit synthetic stars, and we have injected the statistical trend expected from the presence of magma oceans on a fraction of the planets.
    Only a subset of these planets would be detectable by a transit survey, and their properties can be probed only with a finite precision.
    To test the detectability of a magma ocean signature, we simulated several transit surveys with different designs and strategies and explored their capability to recover the magma ocean trend and constrain its parameters.
    We assessed this capability based on two determinants: the likelihood that the mission is able to detect the injected trend, and the precision with which it can constrain the parameters of that trend.
    ...

    We consider a number of key parameters of transit surveys: The telescope's mirror diameter (or effective diameter for a telescope array) $D$, the total time budget of the survey for observations $t_\mathrm{total}$, the maximum number of observed transits for each target $N_\mathrm{obs, max}$, the slew time between observations $t_\mathrm{slew}$, ... \todo[]{double-check which survey params are needed}
